Estimating duration using survival analysis

### 2024-03-25 cis-perfect-testing.tex
plural data
Updates from Overleaf

In \cref{E-ATACCC} I estimated the duration distribution from the ATACCC dataset.
However, this study suffered from a small sample size and only 20 days of follow-up, preventing accurate estimation of the tail.
Therefore, model assumptions drive the size of the estimated tail.

The CIS sampling is less frequent, but with has a large sample size (\numprint{4800} detected infection episodes) and a long follow-up.
Therefore, it is suitable for estimating the tail of the duration distribution.
In this chapter, I develop a method to estimate the duration distribution using CIS data, assuming no false negatives or positives.
Formally, I aim to estimate the survival function $S$ defined in \cref{inc-prev:sec:definitions}.

In \cref{perf-test:sec:problem}, I describe the challenges analysing the data presents.
This motivates using a survival analysis framework which I introduce in \cref{perf-test:sec:surv-analysis}, before deriving the statistical model for the CIS setting in \cref{perf-test:sec:model}.
Next, in \cref{perf-test:sec:parameters-priors}, I consider how to parameterize the survival function and choose priors; these include vague and smoothing priors as well as including information from \cref{E-ATACCC}.
I evaluate the model and priors using a simulation study (\cref{perf-test:sec:simulation-study}), showing that they perform well.
Finally, I discuss the results in \cref{perf-test:sec:discussion}.

@@

The CIS tests each individual infrequently, either weekly or monthly (see \cref{E-intro:sec:cis}), complicating the data in two ways.
First, infection episodes can go undetected.
Second, the infection episodes' start and end times are known imprecisely.
I explain these issues below and devote the rest of the chapter to the development of a method to tackle  them.

@@

The first complication in the analysis is that infection episodes can be undetected.
Undetected infection episodes are episodes with no associated positive tests.
Therefore, there is no information directly observed about the episode; even the number that occur is latent.
They occur when an episode starts and ends between tests (see \cref{perf-test:fig:truncation}).
Undetected episodes are important because they are, on average, shorter than detected episodes; therefore, neglecting them would lead to a biased estimate of the survival distribution.
To see why this is the case, consider the infection episode in figure \cref{perf-test:fig:truncation}.
Here two individuals are shown, with identical data collected for each of them (a series of negative
tests).
The first individual was never infected whereas the second individual has an undetected infection. 
The undetected infection episode begins at time 33 and has a 10-day duration.
The individual would have been detected at their next test if their duration had instead been 24 days or more.
The gap between tests in the CIS (up to 28 days, see \cref{E-intro:sec:cis}) is longer than most infections (median 16 days, see \cref{E-ATACCC:sec:results}).
Therefore, it is likely that many infections in the CIS cohort were undetected.
This is because the interval between tests in the same individual (up to 28 days, see \cref{E-intro:sec:cis}) is longer than most infections (median 16 days, see \cref{E-ATACCC:sec:results}).
\begin{figure}
  \makebox[\textwidth][c]{\includegraphics[width=\textwidth]{cis-perfect-testing/truncation}}
  \caption[Undetected episodes in CIS data]{Graphical illustration of an undetected infection episode, represented by the shaded area. \label{perf-test:fig:truncation}}
\end{figure}

@@

In survival analysis, the interest is in estimating the distribution of the interval between an \emph{initiating event} and a \emph{terminating event}.
In this context, the initiating event is the episode's start; the terminating event is the episode's end.
I start by introducing the relevant, standard concepts in survival analysis; a wide range of texts cover them including \textcite[chapter 1]{bogaertsSurvival}.

A common issue is that the initiating and/or terminating events are not known exactly.
This is known as the event being \emph{censored}.
An event is \emph{left censored} if it is known to occur before a certain time.
An event is \emph{right censored} if it is known to occur after a certain time.
An event is \emph{interval censored} if it is known to occur within an interval.
If both the initiating and terminating event are censored, the data are \emph{doubly censored}.
To handle doubly censored data, the times need to be jointly modelled~\autocite[and references therein]{liSemiparametric}.
If both events are interval censored, then the data are \emph{doubly interval censored}.

Sometimes, only intervals satisfying some property are recorded.
In this case, data are \emph{truncated}.
\emph{Left truncation} is when only events lasting longer than a minimum amount of time are observed.
\emph{Right truncation} is when only events lasting shorter than a maximum amount of time are observed.
Without correcting for the truncation, inference will be biased.

@@

There are also undetected infections in the CIS (see \cref{perf-test:sec:undetected}).
However, the situation is subtly different from the standard truncation situation encountered in the literature.
In the standard situation, nothing is known about the unrecorded intervals.
But in CIS, individuals in which undetected infections occurred are enrolled in the study.
Therefore, we know the times that they were tested.
This provides information on how long their infections may have been.
I refer to these events as ``undetected'', rather than truncated, to emphasise this difference.

@@

For this conditional likelihood to be valid, they assume this conditioning provides negligible information on the distribution of interest~\citePersonalComms{Nick Jewell}.
This assumption performs well in these settings, when the length of the intervals is fairly constant.
In particular, when the interval lengths are near-constant, $p(\text{episode $j$ detected} \mid b_j \in [l_j^{(b)}, r_j^{(b)}]) \approx p(\text{episode $j$ detected})$.
However, the interval lengths change from one to four weeks in the CIS (see \cref{E-intro:sec:cis}).

@@

An individual $i$ has a \emph{test schedule} $\sched_i$.
The test schedule $\sched_i$ is the set of times individual $i$ is tested at, from their last test prior to time 1 (if it exists) up until time $T$.
These are all the times an infection episode can be detected at, plus one prior test
For example, for the individual in \cref{perf-test:sec:undetected}, $\sched_i = \{ 0, 7, 14, 21, 28, 56 \}$.
Each individual has exactly one test schedule, but it is possible that $\sched_i = \sched_{i'}$ for $i \neq i'$.
I assume that the test schedules are uninformative on all quantities of interest because they are part of the study design.
Therefore, I condition on them implicitly in all probabilities that follow.

@@

Any infection episode, whether detected or not, can be fully characterised by the triplet $(b_j, e_j, i(j))$ where $b_j$ and $e_j$ are the times the episode begin and end respectively, and $i(j)$ denotes the individual the episode occurred in.
The episode's duration is $d_j = e_j - b_j + 1$ (see \cref{E-inc-prev:sec:definitions}).
For all $j$, the exact values $b_j$ and $e_j$ are latent.
If $j$ is undetected then $i(j)$ is also latent and nothing is known about $b_j$ or $e_j$.
If $j$ is detected, then $i(j)$ is known; $b_j \in [l_j^{(b)}, r_j^{(b)}]$; and $e_j \in [l_j^{(e)}, r_j^{(e)}]$.
These latter two properties are what make the data doubly interval censored.

@@

\begin{itemize}
\item
  Admissible episodes, $\alpha_i$, which have an infection and recovery time consistent with the data observed.
  This space is empty for $i \notin \set{D}$; in this case individual $i$ had $n_{ia} = 0$ admissible episodes.
  Otherwise, if $i \in \set{D}$, then individual $i$ had $n_{ia} =1$ admissible episode.
  The admissible region is the intersection of the intervals $[l_j^{(b)}, r_j^{(b)}]$ and $[l_j^{(e)}, r_j^{(e)}]$.
  This is the purple area in \cref{perf-test:fig:partitionSpace}; the boundaries in the $x$ direction of the area are $l_j^{(b)}$ and $r_j^{(b)}$ and in the $y$ direction are $l_j^{(e)}$ and $r_j^{(e)}$.
  The shape of this region accounts for the doubly interval censored nature of the data.
  Conditional on the episode occurring in individual $i$, the episode is admissible with probability $p_{ia} = \prob((B_j, E_j) \in \alpha_i \mid \vec{\theta}, i(j) = i)$.
  \label{perf-test:def:admissible}
\item
  Undetected episodes, $\Omega_i$, which have an infection and recovery time such that they would not have tested positive.
  An unknown number, $n_{iu}$ of these occur in individual $i$.
  The undetected region is the red region in \cref{perf-test:fig:partitionSpace}, which are when the individual is infected then recovers before their next test, plus when the individual is infected before their enrolment.
  The shape of this region accounts for the pattern of possible undetected infections.
  Conditional on the episode occurring in individual $i$, the episode is undetected with probability $p_{iu} = \prob((B_j, E_j) \in \Omega_i \mid \vec{\theta}, i(j) = i)$.
\item
  Inadmissible episodes, $\beta_i$, which would be detected (if they occur) but were not.
  Therefore, we know $n_{i\bar{a}} = 0$ of these occurred in individual $i$.
  These are all remaining episodes not in the previous sets.
  Conditional on the episode occurring in these individuals, the episode inadmissible with probability $p_{i\bar{a}} = \prob((B_j, E_j) \in \beta_i \mid \vec{\theta}, i(j) = i)$.
\end{itemize}

@@

% Any episode $j$ independently belongs to one of these classes.
The probabilities ($p_{iu}$, $p_{ia}$, and $p_{i\bar{a}}$), are conditional on the episode occurring in individual $i$.
I assume the individual in which each episode occurs is iid uniform across the cohort.
Therefore, these probabilities are multiplied by $1/\Ncis$ to form the unconditional probabilities.
For example, the probability of an episode being in class $\alpha_i$ is $p_{ia} / \Ncis$.

@@

In forming the region $\alpha_i$, I use the test outcomes.
This is not strictly correct because the cell probabilities in the likelihood should not depend on the data.
However, an alternative considering each combination of infection and recovery times as its own cell is possible.
The new cells would align with the inadmissible region.
Since each of these cells have an observed count of zero, they can be combined to give the same likelihood.
That is, the approach is mathematically equivalent but greatly complicates the formulae and notation.
Therefore, I present this version as it is clearer.

The undetected classes cannot be distinguished.
Therefore, I combine these classes into a single class.
The combined class has a count $\nnodet = \sum_{i=1}^{\Ncis} n_{iu}$ and probability $\pnodet = \frac{1}{\Ncis} \sum_{i=1}^{\Ncis} p_{iu}$.

@@

Therefore, the crucial component is $1 - p_{iu} = 1 - \prob((B_j, E_j) \in \Omega_i \mid \vec{\theta}, i(j) = i)$.
This is one minus the probability that an episode in individual $i$ was undetected, \ie the probability of detecting an episode.

An episode $j$ in individual $i(j)$ is detected if and only if all the following conditions are met.
\begin{enumerate}
    \item $\exists t \in \sched_{i(j)}$ such that $b_j \leq t \leq e_j$; this condition is equivalent to having at least one positive test for the episode.
    \item $\exists t \in \sched_{i(j)}$ such that $t < b_j$.
      For individuals enrolled during the period considered ($\min \sched_{i(j)} > 0$), this ensures that the beginning of the episode is lower bounded; thereby adjusting for those who enrolled during the period being less likely to have a detected infection.
      For individuals enrolled prior to the period considered ($\min \sched_{i(j)} \leq 0$), this means that the episode was not detected prior to time 1.
    \item $\exists t \in \sched_{i(j)}$ such that $t \geq b_j$.
      This means that the test is detected before $T$.
    \item $\exists t \in \sched_{i(j)}$ such that $t > e_j$, upper bounding the end of the episode.
      For episodes detected in the period I consider, this happens a negligible number of times, only in individuals lost to follow-up; therefore, I neglect this possibility.
      For a new context, including recent infections, this condition could be relaxed by considering episodes that do not meet this criterion as right censored.
\end{enumerate}

@@

Uninformative Beta priors on the hazard are problematic in this context.
An uninformative prior would be of the form $\lambda_t \dist \BetaDist(\alpha, \alpha)$.
Commonly, $\alpha$ is chosen to be $0.5$ (Jeffreys' Prior) or $1$ (a uniform prior).
Even though these priors are uninformative on the hazard, they become highly informative on the survival. 
Specifically, they tend to favour shorter survival times (see \cref{perf-test:fig:flat-prior}).
An intuitive explanation of this follows from the fact that priors of this form have an expected value of 0.5.
The expected survival time, $\E \left( \prod_{i=1}^{t-1} (1-\lambda_t) \right)$, is therefore equal to $0.5^{t-1}$, a quantity that declines rapidly.
This prior expresses extreme scepticism in estimates from previous studies, such as \cref{E-ATACCC} and the meta-analysis of \textcite{cevikShedding}.
\begin{figure}
  \centering \includegraphics{cis-perfect-testing/flat-prior}
  \caption[Uninformative priors for the hazard]{
    (A) Density of Beta(1, 1) flat prior and Beta(0.5, 0.5) uninformative priors.
    (B) Prior predictive survival time (mean and 95\% CrI).
    The implied prior on the survival time is short when using either prior on the hazard at each time.
  }
 \label{perf-test:fig:flat-prior}
\end{figure}

@@

Smoothing priors~\autocite{gerschSmoothness} encode the biological consideration that the hazard should not vary significantly from day-to-day.
They serve the same purpose as a penalized likelihood, which is often used in the non-parametric maximum-likelihood setting~\autocite[e.g.][]{bacchettiNonparametric}.
Many possible forms of smoothing priors exist, including splines, Gaussian Processes, and random walks.
I use a second-order random walk (RW2) because it is simple and produces sensible prior predictive distributions.

@@

To form the duration distribution used in the simulation, we combine the two estimates.
The pdf over the first 30 days is proportional to the ATACCC estimate, with the rest proportional to this CIS-based estimate.
Denote by $f_A(t)$ the distribution function estimated in \cref{E-ATACCC} and $f_C(t)$ that from the CIS-based estimates just derived.
Then define:
$$
f_S'(t) = \begin{cases}
	f_A(t) &t \leq 30 \\
	f_C(t) &t > 30
\end{cases}
$$
Then the distribution used in the simulation is the normalised version of this: $f_S(t) = f'_S(t)/\sum_i f_S'(i)$.
These curves and the combined curve are compared in \cref{perf-test:fig:duration-dist}.
Individual $i$'s duration of positivity, $D_i$, is then an independent draw from this distribution.
\begin{figure}
  \centering \includegraphics{cis-perfect-testing/input-duration-dists}
  \caption[Comparison of duration distributions]{Comparison of the duration distribution used for the simulation. ATACCC is the posterior mean from \cref{E-ATACCC}'s analysis, CIS is Sarah Walker's analysis, and Combined is the combination of these used for the simulation. \label{perf-test:fig:duration-dist}}
\end{figure}

>>>>

In \cref{E-ATACCC} I estimated the duration distribution from the ATACCC dataset.
However, this study had a small sample size and only 20 days of follow-up, which prevented accurate estimation of the tail.
Therefore, model assumptions drive the estimated size of the tail.

The CIS samples individuals less frequently, but has a large sample size (\numprint{4800} detected infection episodes) and up to years of follow-up.
Therefore, it is suitable for estimating the tail of the duration distribution.
In this chapter, I develop a method to estimate the duration distribution using CIS data, assuming the test ??? has perfect sensitivity and specificity, {\it i.e.} there are no false negatives or positives.
Formally, I aim to estimate the survival function $S(t)$ defined in \cref{inc-prev:sec:definitions}.

In \cref{perf-test:sec:problem}, I describe the challenges analysing the data presents.
This motivates using a survival analysis framework which I introduce in \cref{perf-test:sec:surv-analysis}, before deriving the statistical model for the CIS setting in \cref{perf-test:sec:model}.
In \cref{perf-test:sec:parameters-priors}, I consider how to parameterize the survival function and choose its priors, including vague and smoothing priors as well as a prior constructed to include the information from \cref{E-ATACCC}.
I evaluate the model and priors using a simulation study (\cref{perf-test:sec:simulation-study}), showing that they perform well.
Finally, I discuss the results in \cref{perf-test:sec:discussion}.

@@

In the CIS, individuals are tested infrequently, either weekly or monthly (see \cref{E-intro:sec:cis}), complicating the data in two ways.
First, infection episodes can go undetected.
Second, the infection episode start and end times are known imprecisely.
I explain these issues below, and devote the rest of the chapter to the development of a method to tackle  them.

@@

The first complication in the analysis is that infection episodes can be undetected.
Undetected infection episodes are episodes with no associated positive tests.
Therefore, there is no information directly observed about the episode; even the number that occur is latent.
They occur when an episode starts and ends between tests (see \cref{perf-test:fig:truncation}).
Undetected episodes are important because they are, on average, shorter than detected episodes; therefore, neglecting them would lead to a biased estimate of the survival distribution.
To see why this is the case, consider the infection episode in figure \cref{perf-test:fig:truncation}.
Here two individuals are shown, with identical data collected for each of them (a series of negative
tests).
The fist individual was never infected whereas the second individual was; but their infection episode was undetected.
The undetected infection episode begins at time 33 and has a 10-day duration.
The individual would have been detected at their next test if their duration had instead been 24 days or more.
The gap between tests in the CIS (up to 28 days, see \cref{E-intro:sec:cis}) is longer than the duration of most infections (median 16 days, see \cref{E-ATACCC:sec:results}).
Therefore, it is likely that many infection in the CIS cohort were undetected.
This is because the interval between tests in the same individual (up to 28 days, see \cref{E-intro:sec:cis}) is longer than most infections (median 16 days, see \cref{E-ATACCC:sec:results}).
\begin{figure}
  \makebox[\textwidth][c]{\includegraphics[width=\textwidth]{cis-perfect-testing/truncation}}
  \caption[Undetected episodes in CIS data]{Graphical illustration of an undetected infection episode, represented by the shaded area. \label{perf-test:fig:truncation}}
\end{figure}

@@

In survival analysis, the interest is in estimating the distribution of the interval between an \emph{initiating event} and a \emph{terminating event}.
In the current context, the initiating event is the episode's start; the terminating event is the episode's end.
I start by introducing the relevant, standard concepts in survival analysis; a wide range of texts cover them including \textcite[chapter 1]{bogaertsSurvival}.

A common issue is that the initiating and/or terminating events are not known exactly.
This is known as the event being \emph{censored}.
An event is \emph{left censored} if it is known to have occurred before a certain time.
An event is \emph{right censored} if it is known to have occurred after a certain time.
An event is \emph{interval censored} if it is known to have occurred within an interval.
If both the initiating and terminating event are interval censored, the data are \emph{doubly interval censored}.
To handle doubly interval censored data, the times need to be jointly modelled~\autocite[and references therein]{liSemiparametric}.

Another important concepts typical of survival data is truncation, which refers to ...?
Sometimes, only intervals satisfying some property are recorded.
In this case, data are \emph{truncated}.
\emph{Left truncation} is when only events lasting longer than a minimum amount of time are observed.
\emph{Right truncation} is when only events lasting shorter than a maximum amount of time are observed.
Without correcting for truncation, inference on the distribution of a duration will be biased.

@@

There is also undetected infections in the CIS (see \cref{perf-test:sec:undetected}).
However, the situation is subtly different from the standard truncation situation encountered in the literature.
In the standard situation, nothing is known about the unrecorded intervals.
But in CIS, individuals in which undetected infections occurred are enrolled in the study.
Therefore, we know the times that they were tested.
This provides information on how long their infections may have occurred.
I refer to these events as ``undetected'', rather than truncated, to emphasise this difference.

@@

For this conditional likelihood to be valid, they assume this conditioning provides negligible information on the distribution of interest~\citePersonalComms{Nick Jewell}.
This assumption performs well in these settings, when the length of the intervals is fairly constant.
In particular, when the interval lengths are near-constant, $p(\text{episode $j$ detected} \mid b_j \in [l_j^{(b)}, r_j^{(b)}]) \approx p(\text{episode $j$ detected})$.
However, in the CIS (see \cref{E-intro:sec:cis}) the interval lengths change from one to four weeks.

@@

An individual $i$ has a \emph{test schedule} $\sched_i$.
The test schedule $\sched_i$ is the set of times individual $i$ is tested at, from their last test prior to time 1 (if it exists) up until time $T$.
This is all the times the infection episode could be detected at and be included, plus one prior test.
For example, for the individual in \cref{perf-test:sec:undetected}, $\sched_i = \{ 0, 7, 14, 21, 28, 56 \}$.
Each individual has exactly one test schedule, but it is possible that $\sched_i = \sched_{i'}$ for $i \neq i'$.
I assume that the test schedules are uninformative on all quantities of interest because they are part of the study design.
Therefore, I condition on them implicitly in all probabilities that follow.

@@

Any infection episode, whether detected or not, can be fully characterised by the triplet $(b_j, e_j, i(j))$ where $b_j$ and $e_j$ are the times the episode begin and end respectively, and $i(j)$ denotes the individual the episode occurred in.
The episode's duration is $d_j = e_j - b_j + 1$ (see \cref{E-inc-prev:sec:definitions}).
For all $j$, the exact values $b_j$ and $e_j$ are latent.
If $j$ is undetected then $i(j)$ is also latent and nothing is known about $b_j$ or $e_j$.
If $j$ is detected, then $i(j)$ is known; $b_j \in [l_j^{(b)}, r_j^{(b)}]$; and $e_j \in [l_j^{(e)}, r_j^{(e)}]$.
These latter two properties are what makes the data doubly interval censored.

@@

\begin{itemize}
\item
  Admissible episodes, $\alpha_i$, which have an infection and recovery time consistent with the data observed.
  This space is empty for $i \notin \set{D}$; in this case individual $i$ had $n_{ia} = 0$ admissible episodes.
  Otherwise, if $i \in \set{D}$, then individual $i$ had $n_{ia} =1$ admissible episode.
  The admissible region is defined by the intersection of the intervals $[l_j^{(b)}, r_j^{(b)}]$ and $[l_j^{(e)}, r_j^{(e)}]$.
  This is the purple area in \cref{perf-test:fig:partitionSpace}; the boundaries in the $x$ direction of the area are $l_j^{(b)}$ and $r_j^{(b)}$ and in the $y$ direction are $l_j^{(e)}$ and $r_j^{(e)}$.
  The shape of this region accounts for the doubly interval censored nature of the data.
  Conditional on the episode occurring in individual $i$, the episode is admissible with probability $p_{ia} = \prob((B_j, E_j) \in \alpha_i \mid \vec{\theta}, i(j) = i)$.
  \label{perf-test:def:admissible}
\item
  Undetected episodes, $\Omega_i$, which have an infection and recovery time such that they would not have tested positive.
  An unknown number, $n_{iu}$ of these occur in individual $i$.
  The undetected region is the red region in \cref{perf-test:fig:partitionSpace}, which are when the individual is infected then recovers before their next test, plus when the individual is infected before their enrolment.
  The shape of this region accounts for the pattern of possible undetected infections.
  Conditional on the episode occurring in individual $i$, the episode is undetected with probability $p_{iu} = \prob((B_j, E_j) \in \Omega_i \mid \vec{\theta}, i(j) = i)$.
\item
  Inadmissible episodes, $\beta_i$, which would be detected (if they occur) but were not.
  Therefore, we know $n_{i\bar{a}} = 0$ of these occurred in individual $i$.
  These are all remaining episodes not in the previous sets.
  Conditional on the episode occurring in these individuals, the episode inadmissible with probability $p_{i\bar{a}} = \prob((B_j, E_j) \in \beta_i \mid \vec{\theta}, i(j) = i)$.
\end{itemize}

@@

% Any episode $j$ independently belongs to one of these classes.
The probabilities ($p_{iu}$, $p_{ia}$, and $p_{i\bar{a}}$), are conditional on the episode occurring in individual $i$.
I assume the individual in which each episode occurs is iid uniform across the cohort.
Therefore, the unconditional probabilities of an infection belonging to a class need to be multiplied by $1/\Ncis$.
For example, the probability of an episode being in class $\alpha_i$ is $p_{ia} / \Ncis$.

@@

In forming the region $\alpha_i$, I use the test outcomes.
This is not strictly correct because the cell probabilities in the likelihood should not depend on the data.
However, an alternative where each combination of infection and recovery times is considered its own cell is possible.
The new cells would align with the inadmissible region.
Since each of these cells have an observed count of 0, they can be combined to give the same likelihood.
That is, the approach is mathematically equivalent but greatly complicates the formulae and notation.
Therefore, I present this version as it is clearer.

The undetected classes cannot be distinguished.
Therefore, these classes can be combined into a single class.
The combined class has a count $\nnodet = \sum_{i=1}^{\Ncis} n_{iu}$ and probability $\pnodet = \frac{1}{\Ncis} \sum_{i=1}^{\Ncis} p_{iu}$.

@@

Therefore, the crucial component is $1 - p_{iu} = 1 - \prob((B_j, E_j) \in \Omega_i \mid \vec{\theta}, i(j) = i)$.
This is one minus the probability that an episode in individual $i$ was undetected, \ie the probability that episode such an episode is detected.

An episode $j$ in individual $i(j)$ is detected if and only if all the following conditions are met.
\begin{enumerate}
    \item $\exists t \in \sched_{i(j)}$ such that $b_j \leq t \leq e_j$; this condition is equivalent to having at least one positive test for the episode.
    \item $\exists t \in \sched_{i(j)}$ such that $t < b_j$.
      For individuals enrolled during the period considered ($\min \sched_{i(j)} > 0$), this ensures that the beginning of the episode is lower bounded; thereby adjusting for those who enrolled during the period being less likely to have a detected infection.
      For individuals enrolled prior to the period considered ($\min \sched_{i(j)} \leq 0$), this means that the episode was not detected prior to time 1.
    \item $\exists t \in \sched_{i(j)}$ such that $t \geq b_j$.
      This means that the test is detected before $T$.
    \item $\exists t \in \sched_{i(j)}$ such that $t > e_j$, upper bounding the end of the episode.
      For episodes detected in the period I consider, this happens a negligible number of times, only in individuals lost to follow-up; therefore, I neglect this possibility.
      For a new context, including recent infections, this condition could be relaxed by considering episodes that do not meet this criteria as right censored.
\end{enumerate}

@@

Uninformative Beta priors on the hazard are problematic in this context.
An uninformative prior would be of the form $\lambda_t \dist \BetaDist(\alpha, \alpha)$.
Commonly, $\alpha$ is chosen to be $0.5$ (Jeffreys' Prior) or $1$ (a uniform prior).
Even though these priors are uninformative on the hazard, they become highly informative on the survival. 
Specifically, they tend to favour shorter survival times (see \cref{perf-test:fig:flat-prior}).
An intuitive explanation of this follows from the fact that priors of this form have an expected value of 0.5.
The expected survival time, $\E \left( \prod_{i=1}^{t-1} (1-\lambda_t) \right)$, is therefore equal to $0.5^{t-1}$, a quantity that declines rapidly.
This prior expresses extreme scepticism in estimates from previous studies, such as \cref{E-ATACCC} and the meta-analysis of \textcite{cevikShedding}.
\begin{figure}
  \centering \includegraphics{cis-perfect-testing/flat-prior}
  \caption[Uninformative priors for the hazard]{
    (A) Density of Beta(1, 1) flat prior and Beta(0.5, 0.5) uninformative priors.
    (B) Prior predictive survival time (mean and 95\% CrI).
    The implied prior on the survival time is very short when using either prior on the hazard at each time.
  }
 \label{perf-test:fig:flat-prior}
\end{figure}

@@

Smoothing priors~\autocite{gerschSmoothness} encode the biological consideration that the hazard should not vary significantly from day-to-day.
They serve the same purpose as a penalized likelihood, which is used frequently in the non-parametric maximum-likelihood setting~\autocite[e.g.][]{bacchettiNonparametric}.
Many possible forms of smoothing priors exist, including splines, Gaussian Processes, and random walks.
I use a second-order random walk (RW2) because it is simple and produces sensible prior predictive distributions.

@@

To form the duration distribution used in the simulation, we combine the two estimates.
The pdf over the first 30 days is proportional to the ATACCC estimate, with the rest proportional to this CIS-based estimates.
% The CIS-based estimates are shifted 3 days in order to make this smooth; this counteracts the above bias of missing the start of the infection (for times above 30 days, the other bias, missing short infections, is negligible). ERR... I'M NOT DOING THIS ANYMORE OH NO!!
Denote by $f_A(t)$ the distribution function estimated in \cref{E-ATACCC} and $f_C(t)$ that from the CIS-based estimates just derived.
Then define:
$$
f_S'(t) = \begin{cases}
	f_A(t) &t \leq 30 \\
	f_C(t) &t > 30
\end{cases}
$$
Then the distribution used in the simulation is the normalised version of this: $f_S(t) = f'_S(t)/\sum_i f_S'(i)$.
These curves and the combined curve are compared in \cref{perf-test:fig:duration-dist}.
Individual $i$'s duration of positivity, $D_i$, is then an independent draw from this distribution.
\begin{figure}
  \centering \includegraphics{cis-perfect-testing/input-duration-dists}
  \caption[Comparison of duration distributions]{Comparison of the duration distribution used for the simulation. ATACCC is the posterior mean from \cref{E-ATACCC}'s analysis, CIS is Sarah Walker's analysis, and Combined is the combination of these used for the simulation. \label{perf-test:fig:duration-dist}}
\end{figure}
